opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-06-20 main.tex
Commited first paragraph in "Our dataset" section from external author
Commited external author contribution

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology,\protect \\
Engler-Bunte-Ring 8, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology,\protect \\ Hermann-von-Helmholtz-Platz 1, 76344 Eggenstein-Leopoldshafen, Germany}
\affil[3]{Department of Aerospace and Mechanical Engineering, University of Southern California, \protect \\3650 McClintock Ave, Los Angeles, CA 90089, USA}
\affil[4]{Department of Chemical Engineering and Materials Science, University of Southern California,\protect \\ 925 Bloom Walk, HED 216, Los Angeles, CA 90089, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Molecular Foundry Division,\protect \\ 1 Cyclotron Rd., Berkeley, 94720 CA, USA}

@@

\input{chapters/02_existing_datasets}

\input{chapters/03_SOTA_ML}

>>>>

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology,\protect \\
Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology,\protect \\ Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[3]{Department of Aerospace and Mechanical Engineering, University of Southern California, \protect \\3650 McClintock Ave, Los Angeles, CA 90089, USA}
\affil[4]{Department of Chemical Engineering and Materials Science, University of Southern California,\protect \\ 925 Bloom Walk, HED 216, Los Angeles, CA 90089, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Molecular Foundry Division,\protect \\ 1 Cyclotron Rd., Berkeley, 94720 CA, USA}

@@

\section{Existing datasets}
\input{chapters/02_existing_datasets}

\section{Machine learning for pXRD}
\input{chapters/03_SOTA_ML}
